---
title: 'Statistical Data Mining: Hierarchical Random Graph and Edge Prediction'
author: "Thankam Abish"
date: "April 28, 2020"
output:
  html_document:
    df_print: paged
---

```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
library(gRain)
library(Rgraphviz)
library(gRbase)
library(ggm)
library(gRim)
library(bnlearn)
library(igraph)
library(igraphdata)
```

### Karate Data
#### Removing 5% of Edges 
##### (Green indicates removed edges)

```{r}
data(karate)
head(karate)
  
kar_edges = gsize(karate) #CHANGE TO KARATE
set.seed(1234)
original = karate #CHANGE to KARATE
randnum = sample(1:kar_edges, ceiling(kar_edges*.05))
randnum <- randnum[order(-randnum)]
g <- karate
missingedge <- g
missingedge <- delete.edges(g, which(E(g)$weight != 0))
for(val in randnum){
  missingedge <- missingedge + edge(as_ids(tail_of(g,E(g)[[val]])), as_ids(head_of(g,E(g)[[val]])))
  g = g - E(g)[val]
}
newg = g
missingedge <- as.undirected(missingedge)
misse <- as.undirected(missingedge)
medge = ceiling(kar_edges*.05)
ghrg <- fit_hrg(g)
plot_dendrogram(ghrg)
pred <- predict_edges(g)
#plot(pred$prob)
E(g)$color <- "gray"
lay <- layout_nicely(g)
gprob <- add_edges(g, t(pred$edges[1:15, ]), color = "red")
gprob2 <- add_edges(gprob, t(pred$edges[16:25,]), color = "orange")
#plot(gprob2, layout = lay)

#ALL PLOTS
E(newg)$color = "red"
E(missingedge)$color = "green"
graph <- graph.union(newg, missingedge)
E(graph)$color <- ifelse(is.na(E(graph)$color_1),E(graph)$color_2,E(graph)$color_1)
graph <- as.undirected(graph)
#plot(graph)
vn <- sub("Actor ", "", V(graph)$name)
V(graph)$label <- vn
x11()
plot(graph)
```

#### Predicted Edges and Hierarchical Random Graph 

```{r}
x11()
plot(gprob2, layout=lay)
x11()
hrg <- fit_hrg(karate)
ihrg <- as.igraph(hrg)
ihrg$layout <- layout.reingold.tilford
plot(ihrg, vertex.size=5, edge.arrow.size=0.2)
```

#### Correctly Predicted Edge Index in Red

```{r}
x11()
#E(missingedge)
x = c(15, 16) #INSERT INDEXES OF MISSING EDGES
#"Actor 3","Actor 10", 
#      "Actor 2", "Actor 20", 
#      "Mr Hi", "Actor 11", 
#      "Mr Hi", "Actor 6")
plot(pred$prob[1:30], xlab = 'Edge Index', ylab = 'Link prediction probability', main = 'Top 30 Link Predictions')
points(x, pred$prob[x], col = "red")
```

#### Removing 15% of Edges 
##### (Green indicates removed edges)

```{r}
data(karate)
head(karate)

kar_edges = gsize(karate) #CHANGE TO KARATE
set.seed(1234)
original = karate #CHANGE to KARATE
randnum = sample(1:kar_edges, ceiling(kar_edges*.15))
randnum <- randnum[order(-randnum)]
g <- karate
missingedge <- g
missingedge <- delete.edges(g, which(E(g)$weight != 0))
for(val in randnum){
  missingedge <- missingedge + edge(as_ids(tail_of(g,E(g)[[val]])), as_ids(head_of(g,E(g)[[val]])))
  g = g - E(g)[val]
}
newg = g
missingedge <- as.undirected(missingedge)
misse <- as.undirected(missingedge)
medge = ceiling(kar_edges*.15)
ghrg <- fit_hrg(g)
plot_dendrogram(ghrg)
pred <- predict_edges(g)
#plot(pred$prob)
E(g)$color <- "gray"
lay <- layout_nicely(g)
gprob <- add_edges(g, t(pred$edges[1:15, ]), color = "red")
gprob2 <- add_edges(gprob, t(pred$edges[16:25,]), color = "orange")
#plot(gprob2, layout = lay)

#ALL PLOTS
E(newg)$color = "red"
E(missingedge)$color = "green"
graph <- graph.union(newg, missingedge)
E(graph)$color <- ifelse(is.na(E(graph)$color_1),E(graph)$color_2,E(graph)$color_1)
graph <- as.undirected(graph)
#plot(graph)
vn <- sub("Actor ", "", V(graph)$name)
V(graph)$label <- vn

x11()
plot(graph)
```

#### Predicted Edges and Hierarchical Random Graph

```{r}
x11()
plot(gprob2, layout=lay)
x11()
hrg <- fit_hrg(karate)
ihrg <- as.igraph(hrg)
ihrg$layout <- layout.reingold.tilford
plot(ihrg, vertex.size=5, edge.arrow.size=0.2)
```

#### Correctly Predicted Edge Index in Red

```{r}
x11()
#E(missingedge)
#pred$edges[1:40,]
x = c(1,9,15,17)#INSERT INDEXES OF MISSING EDGES
plot(pred$prob[1:40], xlab = 'Edge Index', ylab = 'Link prediction probability', main = 'Top 40 Link Predictions')
points(x, pred$prob[x], col = "red")
```

#### Removing 40% of Edges 
##### (Green indicates removed edges)

```{r}
data(karate)
head(karate)

kar_edges = gsize(karate) #CHANGE TO KARATE
set.seed(1234)
original = karate #CHANGE to KARATE
randnum = sample(1:kar_edges, ceiling(kar_edges*.40))
randnum <- randnum[order(-randnum)]
g <- karate
missingedge <- g
missingedge <- delete.edges(g, which(E(g)$weight != 0))
for(val in randnum){
  missingedge <- missingedge + edge(as_ids(tail_of(g,E(g)[[val]])), as_ids(head_of(g,E(g)[[val]])))
  g = g - E(g)[val]
}
newg = g
missingedge <- as.undirected(missingedge)
misse <- as.undirected(missingedge)
medge = ceiling(kar_edges*.40)
ghrg <- fit_hrg(g)
plot_dendrogram(ghrg)
pred <- predict_edges(g)
#plot(pred$prob)
E(g)$color <- "gray"
lay <- layout_nicely(g)
gprob <- add_edges(g, t(pred$edges[1:30, ]), color = "red")
gprob2 <- add_edges(gprob, t(pred$edges[31:55,]), color = "orange")
#plot(gprob2, layout = lay)

#ALL PLOTS
E(newg)$color = "red"
E(missingedge)$color = "green"
graph <- graph.union(newg, missingedge)
E(graph)$color <- ifelse(is.na(E(graph)$color_1),E(graph)$color_2,E(graph)$color_1)
graph <- as.undirected(graph)
#plot(graph)
vn <- sub("Actor ", "", V(graph)$name)
V(graph)$label <- vn

x11()
plot(graph)
```

#### Predicted Edges and Hierarchical Random Graph

```{r}
x11()
plot(gprob2, layout=lay)
x11()
hrg <- fit_hrg(karate)
ihrg <- as.igraph(hrg)
ihrg$layout <- layout.reingold.tilford
plot(ihrg, vertex.size=5, edge.arrow.size=0.2)
```

#### Correctly Predicted Edge Index in Red

```{r}
x11()
#E(missingedge)
#pred$edges[1:40,]
x = c(29,8,12,33,48,42,41,55,35)#INSERT INDEXES OF MISSING EDGES
plot(pred$prob[1:55], xlab = 'Edge Index', ylab = 'Link prediction probability', main = 'Top 55 Link Predictions')
points(x, pred$prob[x], col = "red")
```

### Kite Data
#### Removing 5% of Edges 
##### (Green indicates removed edges)

```{r}
data(kite)
head(kite)

kar_edges = gsize(kite) #CHANGE
set.seed(124345)
original = kite #CHANGE
randnum = sample(1:kar_edges, ceiling(kar_edges*.05))
randnum <- randnum[order(-randnum)]
g <- kite #CHANGE
missingedge <- make_empty_graph() + vertices(LETTERS[1:10])
for(val in randnum){
  missingedge <- missingedge + edge(as_ids(tail_of(g,E(g)[[val]])), as_ids(head_of(g,E(g)[[val]])))
  g = g - E(g)[val]
}
newg = g
missingedge <- as.undirected(missingedge)
misse <- as.undirected(missingedge)
medge = ceiling(kar_edges*.05)
ghrg <- fit_hrg(g)
plot_dendrogram(ghrg)
pred <- predict_edges(g)
#plot(pred$prob)
E(g)$color <- "gray"
lay <- layout_nicely(g)
gprob <- add_edges(g, t(pred$edges[1:5, ]), color = "red")
gprob2 <- add_edges(gprob, t(pred$edges[6:10,]), color = "orange")
#plot(gprob2, layout = lay)

#ALL PLOTS
E(newg)$color = "red"
E(missingedge)$color = "green"
graph <- graph.union(newg, missingedge)
E(graph)$color <- ifelse(is.na(E(graph)$color_1),E(graph)$color_2,E(graph)$color_1)
graph <- as.undirected(graph)
#plot(graph)
vn <- sub("Actor ", "", V(graph)$name)
V(graph)$label <- vn

x11()
plot(graph)
```

#### Predicted Edges and Hierarchical Random Graph

```{r}
x11()
plot(gprob2, layout=lay)
x11()
hrg <- fit_hrg(kite) #CHANGE
ihrg <- as.igraph(hrg)
ihrg$layout <- layout.reingold.tilford
plot(ihrg, vertex.size=5, edge.arrow.size=0.2)

```

#### Correctly Predicted Edge Index in Red

```{r}
x11()
#E(missingedge)
#pred$edges[1:20,]
x = c(5) #CHANGE
#("A", "D")#INSERT INDEXES OF MISSING EDGES
plot(pred$prob[1:10], xlab = 'Edge Index', ylab = 'Link prediction probability', main = 'Top 10 Link Predictions')
points(x, pred$prob[x], col = "red")
```


#### Removing 15% of Edges 
##### (Green indicates removed edges)

```{r}
data(kite)
head(kite)

kar_edges = gsize(kite) #CHANGE
set.seed(124345)
original = kite #CHANGE
randnum = sample(1:kar_edges, ceiling(kar_edges*.15))
randnum <- randnum[order(-randnum)]
g <- kite #CHANGE
missingedge <- make_empty_graph() + vertices(LETTERS[1:10])
for(val in randnum){
  missingedge <- missingedge + edge(as_ids(tail_of(g,E(g)[[val]])), as_ids(head_of(g,E(g)[[val]])))
  g = g - E(g)[val]
}
newg = g
missingedge <- as.undirected(missingedge)
misse <- as.undirected(missingedge)
medge = ceiling(kar_edges*.15)
ghrg <- fit_hrg(g)
plot_dendrogram(ghrg)
pred <- predict_edges(g)
#plot(pred$prob)
E(g)$color <- "gray"
lay <- layout_nicely(g)
gprob <- add_edges(g, t(pred$edges[1:15, ]), color = "red")
gprob2 <- add_edges(gprob, t(pred$edges[16:30,]), color = "orange")
#plot(gprob2, layout = lay)

#ALL PLOTS
E(newg)$color = "red"
E(missingedge)$color = "green"
graph <- graph.union(newg, missingedge)
E(graph)$color <- ifelse(is.na(E(graph)$color_1),E(graph)$color_2,E(graph)$color_1)
graph <- as.undirected(graph)
#plot(graph)
vn <- sub("Actor ", "", V(graph)$name)
V(graph)$label <- vn

x11()
plot(graph)
```

#### Predicted Edges and Hierarchical Random Graph

```{r}
x11()
plot(gprob2, layout=lay)
x11()
hrg <- fit_hrg(kite) #CHANGE
ihrg <- as.igraph(hrg)
ihrg$layout <- layout.reingold.tilford
plot(ihrg, vertex.size=5, edge.arrow.size=0.2)

```

#### Correctly Predicted Edge Index in Red

```{r}
x11()
#E(missingedge)
#pred$edges[1:30,]
x = c(7,30) #CHANGE
#("A", "D")#INSERT INDEXES OF MISSING EDGES
plot(pred$prob[1:30], xlab = 'Edge Index', ylab = 'Link prediction probability', main = 'Top 30 Link Predictions')
points(x, pred$prob[x], col = "red")
```

#### Removing 40% of Edges 
##### (Green indicates removed edges)

```{r}
data(kite)
head(kite)

kar_edges = gsize(kite) #CHANGE
set.seed(124345)
original = kite #CHANGE
randnum = sample(1:kar_edges, ceiling(kar_edges*.40))
randnum <- randnum[order(-randnum)]
g <- kite #CHANGE
missingedge <- make_empty_graph() + vertices(LETTERS[1:10])
for(val in randnum){
  missingedge <- missingedge + edge(as_ids(tail_of(g,E(g)[[val]])), as_ids(head_of(g,E(g)[[val]])))
  g = g - E(g)[val]
}
newg = g
missingedge <- as.undirected(missingedge)
misse <- as.undirected(missingedge)
medge = ceiling(kar_edges*.40)
ghrg <- fit_hrg(g)
plot_dendrogram(ghrg)
pred <- predict_edges(g)
#plot(pred$prob)
E(g)$color <- "gray"
lay <- layout_nicely(g)
gprob <- add_edges(g, t(pred$edges[1:15, ]), color = "red")
gprob2 <- add_edges(gprob, t(pred$edges[16:30,]), color = "orange")
#plot(gprob2, layout = lay)

#ALL PLOTS
E(newg)$color = "red"
E(missingedge)$color = "green"
graph <- graph.union(newg, missingedge)
E(graph)$color <- ifelse(is.na(E(graph)$color_1),E(graph)$color_2,E(graph)$color_1)
graph <- as.undirected(graph)
#plot(graph)
vn <- sub("Actor ", "", V(graph)$name)
V(graph)$label <- vn

x11()
plot(graph)
```

#### Predicted Edges and Hierarchical Random Graph

```{r}
x11()
plot(gprob2, layout=lay)
x11()
hrg <- fit_hrg(kite) #CHANGE
ihrg <- as.igraph(hrg)
ihrg$layout <- layout.reingold.tilford
plot(ihrg, vertex.size=5, edge.arrow.size=0.2)

```

#### Correctly Predicted Edge Index in Red

```{r}
x11()
#E(missingedge)
#pred$edges[1:30,]
x = c(1,12,4,6,7,23,21) #CHANGE
#("A", "D")#INSERT INDEXES OF MISSING EDGES
plot(pred$prob[1:30], xlab = 'Edge Index', ylab = 'Link prediction probability', main = 'Top 30 Link Predictions')
points(x, pred$prob[x], col = "red")
```

